Introduction to LLL\\``Cryptography''

### 2021-05-31 paper.tex
Fix computation of bounds for LLL vs RSA
TODO: Fix numbers with new ones

@@

@@

@@

\begin{center}
    \begin{eqnarray}
        g(x_0) \equiv 0 \mod N^m, |x_0| \le X \label{eq:bound} \\
         \lVert g(xX) \rVert < \frac{N}{\sqrt{n}} \label{eq:pol}
    \end{eqnarray}
\end{center}

@@

Howgrave-Graham's idea is to find this polynomial $g$ by combining polynomials $g_{i,j}$ who also have $x_0$ as roots modulo $N^m$.

@@

\begin{itemize}
    \item It only does \textbf{integer linear operations} on the basis vectors.
        In this way even if the basis is different it's only a linear combination of vector that still have $x_0$ as root
        modulo $N^m$.
    \item If we craft the lattice properly, the norm of shortest vector on the reduced basis will satisfy \ref{eq:pol}.
\end{itemize}

@@

The rows of the matrix correspond to the coefficient vectors of the polynomials $f(x), Nx^2, Nx$ and $N$, furthermore we know
that each polynomials will be 0 modulo $N$ if evaluated at $x = m$.
We didn't fully applied Howgrave-Graham because we only used $m=1$ (the $N^m$ parameter not the message).\\
With this lattice construction every vector is of the form $v = (v_1X^3, v_2X^2, v_1X, v_0)$, because any
integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=0,..,\dim(B)-1$.

@@

\[
    \lVert g(xX) \rVert \le \frac{N}{\sqrt{n+1}}
\]

In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 1.02^n (\det B)^{\frac{1}{dimB}}$.
If we ignore the $1.02^n$ factor, then we need to satisfy that

\[
    g(m) \le \lVert v \rVert \le (\det B)^{\frac{1}{4}} < X
\]

@@

We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < N$, if we solves for $X$ this will be satisfied when $X < N^{\frac{1}{6}}$.
In this case we have $N = 100$-bit number and $X = 2^{16}$, so $N^{\frac{1}{6}} > X$ and we have verified the correctness.\\

>>>>

\subsection{Algorithm}

@@

\subsection{Security}

RSA relies on the hardness of factoring the modulo $N$ and we don't have a polynomial algorithm to factor it, so it's considered secure.
However there are different attacks against textbook RSA or a relaxed model of RSA:

\begin{enumerate}
    \item If $m < N^{\frac{1}{e}}$, then $m^e < N$ and the modulo operation is not applied and we only need to find the $e$th root of $c$ over the
        integers to find $m$.
    \item If $q = p + x$ where $x$ is small enough than it's easy to recover the factors of $N$ computing $A = \sqrt{N}$ and compute
            $p = A - x$ for different value of $x$ until $N \mod p = 0$, then we have found $q = N / p$
    \item Many more attacks can be found TODO.
\end{enumerate}

@@

We want to attack a relaxed model of RSA where we know a part of the message $m$.
We start introducing the \ref{TODO} coppersmith attack and the math behind it.

\subsection{Mathematical introduction}

@@

\begin{center}
    \begin{eqnarray}
        g(x_0) \equiv 0 \mod N^m, |x_0| \le X \label{eq:bound} \\
         \lVert g(xX) \rVert < \frac{N^m}{\sqrt{n}} \label{eq:pol}
    \end{eqnarray}
\end{center}

@@

Howgrave-Graham's idea is to find this polynomial $g$ by combining polynomials $p_i$ who also have $x_0$ as roots modulo $N^m$.

@@

\begin{itemize}
    \item It only does \textbf{integer linear operations} on the basis vectors.
        In this way even if the basis is different it's only a linear combination of vector that still have $x_0$ as root
        modulo $N^m$.
    \item If we craft the lattice properly, the norm of shortest vector on the reduced basis will satisfy \ref{eq:pol}.
        We know the length's bound of the shortest vector that LLL could find.
\end{itemize}

@@

The rows of the matrix correspond to the coefficient vectors of the polynomials $f(x), Nx^2, Nx$ and $N$, furthermore we know
that each polynomials will be 0 modulo $N$ if evaluated at $x = m$.
We applied Howgrave-Graham with $m=1$ (the $N^m$ parameter not the message).\\
With this lattice construction every vector is of the form $v = (v_1X^3, v_2X^2, v_1X, v_0)$, because any
integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=0,..,\dim(B)-1$.

@@

\[
    \lVert g(xX) \rVert \le \frac{N}{\sqrt{n}}
\]

In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 2^{\frac{n(n-1)}{4(n)}} (\det B)^{\frac{1}{n}}$.
If we ignore the $2^{\frac{3}{4}}$ factor (remember that $n = 4$), then we need to satisfy that

\[
    g(m) \le \lVert v \rVert \le (\det B)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}
\]

@@

We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solves for $X$ this will be satisfied when $X < (\frac{N}{16})^{\frac{1}{6}}$.
With the numbers we have this inequality is verified, however even if the bound of the shortest vector is larger we still have some possibilities to
find the correct root.
